A unified model for parsing and sentence understanding

### 2016-03-14 writing/hard_stack_paper/paper.tex
Add some more detail to The Big Sentence in the introduction

In this paper, we introduce the Parser--Interpreter Neural Network, or PINN. The PINN is a model which reimplements tree-structured composition within an alternative design that incorporates a neural network parser. This design improves upon the previous TreeRNN approach to compositionality in three ways:
\begin{itemize}
\item At test time, it can simultaneously parse and interpret unparsed sentences, removing the dependence on an external parser.
\item It supports batched computation for both parsed and unparsed sentences, supporting dramatic speedups over standard TreeRNNs.
\item It supports a novel tree-sequence hybrid mechanism for handling local context in sentence interpretation that yields substantial gains in accuracy over either pure sequence-based models or pure tree-based models.
\end{itemize}

>>>>

In this paper, we introduce the Parser--Interpreter Neural Network, or PINN. The PINN executes tree-structured computations in a linearized sequence, and can incorporate a neural network parser that determines the overall tree structure on-the-fly. This design improves upon the previous TreeRNN approach to compositionality in three ways:
\begin{itemize}
\item At test time, it can simultaneously parse and interpret unparsed sentences, removing the dependence on an external parser.
\item It supports batched computation for both parsed and unparsed sentences, supporting dramatic speedups over standard TreeRNNs.
\item It supports a novel tree-sequence hybrid mechanism for handling local context in sentence interpretation that yields substantial gains in accuracy over either pure sequence-based models or pure tree-based models.
\end{itemize}
